A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol

### 2023-04-09 paper.tex
removed accidental ~ in headings

\hypertarget{statistical-significance}{%
\subsection{\texorpdfstring{Statistical
significance\textasciitilde{}\label{sig}}{Statistical significance\textasciitilde{}}}\label{statistical-significance}}

@@

\hypertarget{power-comparison-of-the-tests}{%
\subsection{\texorpdfstring{Power comparison of the
tests\textasciitilde{}\label{power-analysis}}{Power comparison of the tests\textasciitilde{}}}\label{power-comparison-of-the-tests}}

@@

\hypertarget{comparison-of-test-decisions-based-on-p-values}{%
\subsection{\texorpdfstring{Comparison of test decisions based on
\(p\)-values\textasciitilde{}\label{p-value}}{Comparison of test decisions based on p-values\textasciitilde{}}}\label{comparison-of-test-decisions-based-on-p-values}}

@@

\hypertarget{effect-of-amount-of-non-linearity}{%
\subsection{\texorpdfstring{Effect of amount of
non-linearity\textasciitilde{}\label{nonlin-analysis}}{Effect of amount of non-linearity\textasciitilde{}}}\label{effect-of-amount-of-non-linearity}}

@@

\hypertarget{effect-of-shape-of-heteroskedasticity}{%
\subsection{\texorpdfstring{Effect of shape of
heteroskedasticity\textasciitilde{}\label{hetero-analysis}}{Effect of shape of heteroskedasticity\textasciitilde{}}}\label{effect-of-shape-of-heteroskedasticity}}

>>>>

\hypertarget{statistical-significance}{%
\subsection{\texorpdfstring{Statistical
significance\label{sig}}{Statistical significance}}\label{statistical-significance}}

@@

\hypertarget{power-comparison-of-the-tests}{%
\subsection{\texorpdfstring{Power comparison of the
tests\label{power-analysis}}{Power comparison of the tests}}\label{power-comparison-of-the-tests}}

@@

\hypertarget{comparison-of-test-decisions-based-on-p-values}{%
\subsection{\texorpdfstring{Comparison of test decisions based on
\(p\)-values\label{p-value}}{Comparison of test decisions based on p-values}}\label{comparison-of-test-decisions-based-on-p-values}}

@@

\hypertarget{effect-of-amount-of-non-linearity}{%
\subsection{\texorpdfstring{Effect of amount of
non-linearity\label{nonlin-analysis}}{Effect of amount of non-linearity}}\label{effect-of-amount-of-non-linearity}}

@@

\hypertarget{effect-of-shape-of-heteroskedasticity}{%
\subsection{\texorpdfstring{Effect of shape of
heteroskedasticity\label{hetero-analysis}}{Effect of shape of heteroskedasticity}}\label{effect-of-shape-of-heteroskedasticity}}
